Country-Level Impact of Education on Entrepreneurship

### 2014-12-11 PresentationandPaper/FromEducationToEntrepreneurship.Rmd
Paper Update

Specifically, we expect to find out to what extent positive reinforcement in teaching can impact the rate of entrepreneurship at a country level, especially across OECD countries. Indeed, regarding France and the United Kingdom, many parameters differ between the two education systems but one stands out, that is the positive reinforcement. Indeed, while positive reinforcement is effectively in use throughout the compulsory education system in the UK, but it is much more rarely activitated in France, and only on an voluntary individual teacher's basis. We would like to verify if this has to do with the amount of entrepreneurial self-efficacy mentioned above, in which case this could also affect entrepreneurial intentions, behaviours and actions.

This assumption draws from Boyd and Vozikis's ??????? MAIN BIB ???????? stating how entrepreneurial intentions are at least partially the result of thought processes, which " underlie the creation of formal business plans, opportunity analysis, and goal-directed behaviour". Boyd and Vosikis also assert that individual self-efficacy "influences the development of both entrepreneurial intentions and actions or behaviours". To assert this, they rely on Fishbein and Ajzen 1975 ?????? MAIN BIB ???????? who illustrate the relation between beliefs and behaviour as follows:

@@

Now, since self-confidence is considered to rely partly on one's integration within social networks [@OECD2009]

>>>>

Specifically, we expect to find out to what extent positive reinforcement in teaching can impact the rate of entrepreneurship at a country level, especially across OECD countries. Indeed, regarding France and the United Kingdom, many parameters differ between the two education systems but one stands out, that is the positive reinforcement. Indeed, while positive reinforcement is effectively in use throughout the compulsory education system in the UK, it is much more rarely activitated in France, and only on an voluntary individual teacher's basis. We would like to verify if this has to do with the amount of entrepreneurial self-efficacy mentioned above, in which case this could also affect entrepreneurial intentions, behaviours and actions.

This assumption draws from Boyd and Vozikis's ??????? MAIN BIB ???????? stating how entrepreneurial intentions are at least partially the result of thought processes, which "underlie the creation of formal business plans, opportunity analysis, and goal-directed behaviour". Boyd and Vosikis also assert that individual self-efficacy "influences the development of both entrepreneurial intentions and actions or behaviours". To assert this, they rely on Fishbein and Ajzen 1975 ?????? MAIN BIB ???????? who illustrate the relation between beliefs and behaviour as follows:

@@

Now, since self-confidence is considered to rely partly on one's integration within social networks [@OECD2009] we should ideally be looking into the collectivism or individualism at play across education systems, the more so as there is visibly something at stake on that side too as shows this table:
